Inefficient Concessions and Mediation

### 2017-09-14 draft.tex
add intuitive criterion as justification for focus on best eqm for high types

\begin{theorem}
	The strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.
	\label{theorem:1}
\end{theorem}
\emph{Proof}: See appendix.
\\
\\
In this equilibrium two mutually distrustful countries go ahead and behave as if they trust anyway, taking a risk. This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small.  This is representative of a case where countries have suspicions about each other, but proceed anyway.

@@

>>>>

\begin{theorem}
	The strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.
	\label{theorem:1}
\end{theorem}

\emph{Proof}: See appendix.
\\
In this equilibrium, two mutually distrustful countries go ahead and behave as if they trust anyway, taking a risk. This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small.  This is representative of a case where countries have suspicions about each other, but proceed anyway.

@@

This `best' concessions separating equilibrium, where `best' is from the standpoint of high-type welfare, is justified by appeal to the Intuitive Criterion equilibrium refinement, in which out of equilibrium beliefs put zero weight on types that can never gain from deviating.
